---
title: "HW1"
author: "Edward Zhang"
date: "1/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=4)
options(scipen = 0, digits = 3)  # controls base R output
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(ggplot2, dplyr, tidyverse, gridExtra, ggrepel, plotly, skimr, tidytext) 
# install a package if it does not exist already and put the package in the path (library)
# dplyr, ggplot2,tidyr
```

## Case 1: Audience Size
### 2.1 Data Preparation
#### i. Selecting variables of Interest
```{r Data Cleaning}
surveyResults <- read.csv('Survey_results_final.csv')
filtered <- surveyResults[, c(28, 29, 30, 31, 32, 33, 10)]
newNames <- c('age', 'gender', 'education', 'income', 'sirius', 'wharton', 
              'worktime')

for (idx in 1:7){
  names(filtered)[idx] <- newNames[idx]
}

realGender <- filtered[, 'education']
realEdu <- filtered[, 'gender']

filtered[, 'education'] <- realEdu
filtered[, 'gender'] <- realGender
```

#### ii. Handling incorrectly filled data
The initial dataset seemed to have education and gender values that were 
swapped. This was resolved by simply swapping their values.

```{r Inspection}
  cnt <- 1
  for (elt in filtered$wharton){
    if (elt == "Yes"){
      filtered[cnt, "sirius"] <- "Yes"
    }
    cnt <- cnt + 1
  }
    
```

Furthermore, I went through all the affirmative answers for listening to
Wharton and made sure that its corresponding response to listening to Sirius
was also affirmative because Wharton's show is literally broadcast on the 
Sirius channel.

```{r Subset Confirmation}
  filtered[1008, "age"] <- "18"
  filtered[664, "age"] <- "22"
  filtered[1535, "age"] <- "27"
  filtered <- filtered[-c(886, 479, 663, 
                          1018, 1251, 1261, 1386, 1643, 
                          100, 497, 764, 784, 963,
                          261, 559, 578,
                          856, 1481),]
  
  filtered$age <- as.numeric(filtered$age)
```

The column of Age appears to be a character string which does not really make
any sense. In sorting it, we find that there are 4 incorrect entries. Since
there are a total of 1764 data points to work with, I will simply tossed out 
two of those bad entries and corrected the other two
(eighteen(18) -> 18, 27' -> 27).

Someone also reported to be 223, so I made then 22. Once that was done, I 
converted that column into numerical typings.

Looking at the gender results, six additional people left that field blank, so
I removed them from the dataset.

Looking at education results, a couple people didn't actually select an option,
but we'll keep that for now.

Looking at income, five people left that field blank, so they were removed.

Looking at sirius listenership, three people left it blank. Since they also did
not listen to wharton, we cannot be sure if they listened to sirius or not. Thus
they were removed as well.

Looking at wharton's listenership, two people left it blank, and based on their
sirius listenership, we cannot determine whether or not they listened to wharton
or not.

There were no issues with the worktime field as that is processed by MTurk.

#### iii. Summary

```{R Misc, echo = FALSE}
  summary(filtered)
  
  age <- filtered$age
  hist(age)
  
  generatePChart <- function(list, title){
      list <- sort(list) 
    
      boxCnts <- c()
      boxes <- c()
      prev <- list[1]
      currBoxCnt <- 0
      for (x in list){
        if (prev == x){
          currBoxCnt <- currBoxCnt + 1
        } else {
          boxCnts <- append(boxCnts, currBoxCnt)
          boxes <- append(boxes, prev)
          currBoxCnt <- 1
          prev <- x
       }
      }
    
    boxCnts <- append(boxCnts, currBoxCnt)
    boxes <- append(boxes, prev)
    
    lbls <- boxes
    pct <- round(boxCnts/sum(boxCnts)*100)
    lbls <- paste(lbls, pct) # add percents to labels
    lbls <- paste(lbls,"%",sep="") # ad % to labels
    pie(boxCnts, labels = lbls, main= title)
  }
  
  generateBChart <- function(list, title){
      list <- sort(list) 
    
      boxCnts <- c()
      boxes <- c()
      prev <- list[1]
      currBoxCnt <- 0
      for (x in list){
        if (prev == x){
          currBoxCnt <- currBoxCnt + 1
        } else {
          boxCnts <- append(boxCnts, currBoxCnt)
          boxes <- append(boxes, prev)
          currBoxCnt <- 1
          prev <- x
       }
      }
    
    boxCnts <- append(boxCnts, currBoxCnt)
    boxes <- append(boxes, prev)
    
    df <- data.frame(
      categories = boxes,
      value = boxCnts
    )
    
    ggplot(df, aes(x=categories, y=value)) + 
    geom_bar(stat = "identity")
  }
  
  
  generatePChart(filtered$gender, "Gender Breakdown")
  generatePChart(filtered$education, "Education Breakdown")
  generatePChart(filtered$income, "Income Breakdown")

  
  
```
&nbsp; 

The respondants to this survey seem to consist of mainly young people with
low to moderate levels of income. There are slightly more men than women that
responded, and very few people that responded had any education beyond that of
a Bachelor's degree. This generally paints our pool of respondents as mostly
college aged students and young adults in the process of transitioning into the
workforce.


### 2.2 Sample Properties
#### Comparison to General US Population
50.8% of the US population is female which contrasts with the 58 - 42 Male -
Female split shown in our sample pool. Our sample is much younger than the 
US population at large, with a major under representation of the 60-69 year old
population in favor of the 20 to 40 year old portion of the population. 

However, within that 20-40 year old portion of our sample size (in which the 
majority of our respondents came from), our sample reflects the educational 
levels of the general US populace as of 2019 with a slight over representation 
within the grouping of holders or graduate/professional degrees.

In terms of income, our MTurk sample averages a lower general income level 
compared to the percentage distribution of household income in the US as of 
2020, with only 3% of our sample making over 150K per year where as over 18% of 
American households make 150K or more per year. This discrepancy can likely be 
explained by the notion that people with lower levels of income would be more 
predisposed to embrace gig work like that of MTurk.

Thus, our sample is not a perfect representation of the general US population. 
More-so, our sample more specifically reflects a more educated and male, but lower
income portion of the US population.

#### Comparison to the MTurk Population
MTurk's userbase skews even more female than the general US population, with 
roughly 58% of its userbase being female, clashing even more with our sample's 
male majority. However, in terms of age, our sample is much more in line with
the distribution of MTurker ages, though our sample remains slightly younger than
MTurk as a whole.  

In terms of education, MTurk's general education level is fairly well reflected
in the education levels of the our sample, with roughly 91% of the general MTurk
population having had at least some college experience as opposed to the 88% 
found in our research sample.

Regarding income, our sample's income levels reflect the trends found in the 
general MTurk population very well, though it still under performs MTurk by a 
little. This might coincide with the fact that our sample was generally younger
than the overall MTurk population.

Overall, our sample is much more reflective of the MTurk population than it is 
of the general US population, to the point where it might even be within the 
margin of error for being considered as a representative random sample of the 
MTurk population. Though while it may be functionally equivalent to being a random
sample of the MTurk population, it is likely that the pricing of this task was 
what drove the general age and income of its respondents downward.

Sources: 

Hanson, Melanie. “Education Attainment Statistics” EducationData.org, November 22, 2021,
https://educationdata.org/education-attainment-statistics

“Mechancial Turkers: Young, Well-Educated and Frequent Users.” Pew Research Center: Internet, Science &amp; Tech, Pew Research Center, 30 May 2020, https://www.pewresearch.org/internet/2016/07/11/turkers-in-this-canvassing-young-well-educated-and-frequent-users/. 

Moss, Aaron, and Leib Litman. “Demographics of People on Amazon Mechanical Turk.” CloudResearch, 10 Aug. 2020, https://www.cloudresearch.com/resources/blog/who-uses-amazon-mturk-2020-demographics/. 

U.S. Census Bureau 2019. QuickFacts

“U.S. Income Distribution 2019.” Statista, 21 Sept. 2021, 
https://www.statista.com/statistics/203183/percentage-distribution-of-household-income-in-the-us/. 

### 2.3 Final Estimate
Since our previous 
```{R Estimation}
#There are are roughly 51.6 Million SiriusXM 
#In order to listen to the Wharton show, one MUST be listening on SiriusXM
#Thus, the percentage of SiriusXM listeners that listen to Wharton should be
#our overall percentage.

idx = 1

yesCnt = 0
noCnt = 0

for (x in filtered$sirius){
    if (x == "Yes"){
      if (filtered$wharton[idx] == "Yes"){
        yesCnt <- yesCnt + 1
      } else {
        noCnt <- noCnt + 1
      }
    }
    idx <- idx + 1
}

listenerBreakdown <- c(yesCnt, noCnt)
labels <- c("Listen to Wharton on Sirius", "Do not listen to Wharton on Sirius")

pct <- round(listenerBreakdown/sum(listenerBreakdown)*100)
labels <- paste(labels, pct) # add percents to labels
labels <- paste(labels,"%",sep="") # ad % to labels
pie(listenerBreakdown, labels = labels, main= "Proportion of Sirius Listeners that Listen to Wharton's Sirius Talkshow")

.05 * 51.6

```
Based on our results, 5% of SiriusXM listeners listen to the Wharton show, 
meaning that roughly 2.58 million people listen to Wharton's show.

#### Executive Summary
1. Goal of the study
The goal of this study was to estimate the total number of people that listen to
Wharton's SiriusXM talk show.

2. Method used
Data was collected by putting out a task on Amazon Mechanical Turk in which 
people were first asked whether or not they listened to SiriusXM, and second 
asked whether or not they listened Sirius Business Radio by Wharton. Turkers 
were paid 10 cents to complete this task, but were prevented from doing it twice
to ensure no duplicates. Given that the sample of respondents represented the MTurk platform at a whole
fairly well, and that MTurk represented the US population fairly well, we estimated
the percentage of SiriusXM listen to the Wharton Talk show would be reflective
of the true percentage.

3. Findings
Based on our findings and after cleaning the data, we found that roughly 5% of
the people in our sample that listened to SiriusXM also listened to Sirius
Business Radio. Thus, we estimate that about 5% of the 51.6 million Sirius 
XM listeners listen to the Wharton show.

4. Limitations of the Study
Due to the fact that our sample size is significantly younger in age and lower
in terms of income than the general US public, it is possible that our results
have been skewed towards the views of the younger, less experienced, and more
educated population of America. Plus, the sample size simply may have been too
small to account for random biases based on the MTurkers who would have decided
to do this task for the 10 cents it offered.













